Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-13 Paper/paper.tex
Jed edited a bit in discussion and a few other small places

some filtering is controlled by non-central provincial ASes. China has a

@@

Chinese provincial network. The potential for various forms of censorship in

@@

% Points of Presence
\subsection{Other Chokepoint Measures}
There are several ways that a country can create chokepoints, either intentionally or accidentally: taking advantage of Internet Exchange Points (IXPs),
limiting the number of physical connections that cross the border, or working with---and supporting---a s,a;; set pf ;arge ISPs that have international connections.
Each of these combines two basic elements: limiting the number of organizations that the government must interact with and creating physical locations where traffic can be controlled.
We chose to define chokepoint potential in terms of the AS graph instead of physical locations because the AS graph captures the most interesting physical attributes of the Internet, and
virtualization of the physical and datalink layers on the Internet make physical locations less meaningful. A single undersea cable can be multiplexed to serve as several different links in
the AS graph, and ASes in one country can have physical Points of Presence (PoPs) in several other countries (e.g., China Telecom in Pasadena, California). Thus, the AS graph is a good approximation
of overall chokepoint potential, and information such as geography and the physical locations of routers does not add meaningfully to the analysis without considering every individual piece of Internet
infrastructue on a case-by-case basis. Additionally, the dramatic shifts in chokepoint potential over time depicted in our analysis are unrelated to constant geography, so our AS-level study is important
to show time evolution of chokepoints.

>>>>

some filtering at the time of the study was controlled by non-central provincial
ASes. China had a

@@

Chinese provincial network, but this may have changed since. The potential for various forms of censorship in

@@

% Points of Presence
\subsection{Other Chokepoint Measures}
There are several ways that a country can create chokepoints, either intentionally or accidentally: taking advantage of Internet Exchange Points (IXPs),
limiting the number of physical connections that cross the border, centralizing
the DNS infrastructure within the country, or working
with---and supporting---a set of ISPs that have international connections.
Each of these combines two basic elements: limiting the number of organizations that the government must interact with and creating physical locations where traffic can be controlled.
We chose to define chokepoint potential in terms of the AS graph instead of physical locations because the AS graph captures the most interesting physical attributes of the Internet, and
virtualization of the physical and datalink layers on the Internet make physical locations less meaningful. A single undersea cable can be multiplexed to serve as several different links in
the AS graph, and ASes in one country can have physical Points of Presence (PoPs) in several other countries (e.g., China Telecom in Pasadena, California). Thus, the AS graph is a good approximation
of overall chokepoint potential, and information such as geography and the physical locations of routers does not add meaningfully to the analysis without considering every individual piece of Internet
infrastructue on a case-by-case basis. Additionally, the dramatic shifts in chokepoint potential over time depicted in our analysis are unrelated to constant geography, so our AS-level study is important
to show time evolution of chokepoints.

The DNS infrastructure is another potential graph where chokepoints can be
exploited for censorship and surveillance\~cite{Greschbach2016a} and is at a
higher layer in the network stack than IP routes.  However, we leave analysis of
this graph for future work because it is outside the scope of \toolname and
because the countries that rely on DNS as their main form of censorship are
fewer in number and are among the least sophisticated in terms of their
censorship regime.
